Hydra Battles and Cie

### 2021-06-30 doc/part-hydras.tex
resolve mistakes

\vspace{4pt}
\noindent\emph{From Library~\href{../theories/html/hydras.OrdinalNotations.ON_mult.html}{OrdinalNotations.ON\_Generic}}

@@

The following lemma is an application of the strict inequality 
$\alpha < \omega ^\alpha.$ If \alpha is strongly accessible, then, by definition,
$\omega^\alpha$ is accessible, thus \alpha is \emph{a fortiori} accessible.

>>>>

\vspace{4pt}
\noindent\emph{From
Library~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{OrdinalNotations.ON\_Generic}}

@@

The following lemma is an application of the strict inequality 
$\alpha < \omega ^\alpha$. If $\alpha$ is strongly accessible, then, by definition,
$\omega^\alpha$ is accessible, thus $\alpha$ is \emph{a fortiori} accessible.
